\documentclass[runningheads]{llncs}

\usepackage{booktabs}
\usepackage{listings}
\usepackage{url}
\usepackage{xspace}

\input{coq-listings}

\lstset{
  basicstyle=\ttfamily\small,
  columns=fullflexible,
  keepspaces=true,
  breaklines=true,
  frame=single,
  xleftmargin=0.5em,
  xrightmargin=0.5em
}

\setlength{\intextsep}{1em}

\IfFileExists{generated/results.tex}
  {\input{generated/results.tex}}
  {\input{write_up/generated/results.tex}}

\title{Engineering Certified JSON Derivers for Rocq with ELPI}
\titlerunning{Certified JSON Derivers for Rocq}

\author{Will Thomas \and Perry Alexander}

\authorrunning{W. Thomas, P. Alexander} % Abbreviated for headers

\institute{University of Kansas, Lawrence, USA\\
\email{\{30wthomas, palexand\}@ku.edu}}

\newcommand{\coqelpi}{\texttt{coq-elpi}\xspace}

\begin{document}
\maketitle

\begin{abstract}
  Practical verification produces extracted code, and extracted code eventually
  crosses system boundaries.  JSON is a common boundary format for
  configuration, test data, counterexamples, traces, and tool pipelines, but
  serializers at this boundary are often hand-written and unverified.  We
  present an ELPI-based deriver for JSON that automatically generates
  \texttt{Jsonifiable} instances for a practical fragment of Rocq inductive and
  record types.  Each generated instance contains an encoder, a decoder, and a
  Rocq-checked proof that decoding the encoded value recovers the original.  The
  contribution is a performance-conscious tool for extending the verified trust
  perimeter of extracted Rocq components to their JSON boundary.  The tool is
  distributed as the \texttt{rocq-json} opam package.
\end{abstract}

\section{Introduction}

Automated verification is often evaluated by the proof it produces, but
practical formal methods also has to run.  A verified component may be extracted
to OCaml, linked into a test harness, used as a runtime monitor, embedded in a
larger tool chain, or deployed as part of a verified system.  As soon as that
component communicates with the outside world, the proof assistant's internal
data representation crosses a boundary.

JSON is a common format at that boundary.  Model-checker front-ends exchange
structured system descriptions and counterexamples, verified runtime monitors
consume event logs, test generators exchange inputs and results, and verified
protocols serialize messages for unverified peers.
The problem is that the serialization layer is often outside the trusted
development.  Extraction preserves the behavior of Rocq \cite{rocqDevs:2025:rocq_9.0.0} terms, but it does not
automatically certify the hand-written encoder or decoder that maps those terms
to a deployment format.  A bug in that code can invalidate the deployed verification story.

As a concrete example, consider a verified runtime monitor extracted from a
Rocq specification.  The monitor may consume JSON event logs produced by an
unverified system, or emit JSON counterexample traces for an external
visualizer.  If the boundary type is an event record with a tag, timestamp, and
payload, then a hand-written decoder that swaps fields, drops a constructor, or
accepts a malformed encoding can make the deployed monitor reason about a value
different from the one represented at the JSON boundary.  The Rocq proof still
holds internally, but the deployment guarantee has moved outside the proof.
For outbound traces, the \texttt{canonical\_jsonification} theorem rules out
this class of encoder/decoder mismatch at Rocq compile time: every value emitted
by the verified component decodes back to the original Rocq value.

\texttt{rocq-json} addresses this gap by extending the formal trust perimeter to
the JSON boundary.  It provides the following typeclass:

\begin{lstlisting}[language=Coq]
Class Jsonifiable (A : Type) := {
  to_JSON     : A -> JSON;
  from_JSON   : JSON -> Result A string;
  canonical_jsonification : forall (a : A), from_JSON (to_JSON a) = res a
}.
\end{lstlisting}

The deriver described here generates all three components for many ordinary
inductive and record types.  It is implemented in \coqelpi and exposed through
the command \texttt{Elpi derive.jsonifiable T} \cite{Tassi:2025:ELPI}. For verification-oriented
applications that produce JSON, the central guarantee is exactly the displayed
one: a value that leaves the verified component through the encoder can be
decoded back to the same Rocq value.

This is a tool paper about practical verification engineering with code that
may cross assurance boundaries.
The substantially new contribution is the integration of ELPI
inspection of Rocq declarations, generated code that remains suitable for
extraction, typeclass parameters for nested serializable fields, automatic proof
construction for the round-trip theorem, and an artifact that measures both
applicability and extracted performance.  The same ingredients are broadly
useful for other derivers that construct computational content and accompanying
correctness proofs.

\paragraph{Availability.}
The tool is available as the \texttt{rocq-json} opam package.  The public
development repository and review artifact are available at
\url{https://github.com/ku-sldg/rocq-json}.

\section{Tool Overview}

The user-facing interface is deliberately small.  Given a declaration such as an
enumeration, algebraic data type, parameterized container, or record, the user
invokes the deriver and receives a registered typeclass instance.  Nullary
constructors are encoded as JSON strings.  Constructors with arguments are
encoded as singleton JSON objects whose key is the constructor name and whose
value stores named fields.\footnote{For anonymous arguments, the deriver uses
  the first character of the argument type's head constructor name as a base key.  Duplicate
  base keys are disambiguated with numeric suffixes, so two anonymous
  \texttt{nat} fields become \texttt{n1} and \texttt{n2}.}
Records are encoded as JSON objects keyed by projection names.

For example, the following declaration and command are enough to produce an
encoder, decoder, proof of \emph{invertibility}, and registered typeclass instance:

\begin{lstlisting}[language=Coq]
Inductive UserRole : Type :=
| Admin   | Guest   | Moderator (level : nat)
| StandardUser (id : nat) (username : string).
Elpi derive.jsonifiable UserRole.
\end{lstlisting}

The generated representation uses a string for nullary constructors and an
object for constructors with fields:

\begin{lstlisting}[language=Coq]
Example role_roundtrip (r : UserRole) :
  from_JSON (to_JSON r) = res r := canonical_jsonification r.
Example moderator_json :
  to_JSON (Moderator 2) = JSON_Object [
    ("Moderator", JSON_Object [("level", JSON_Nat 2)])] := eq_refl.
\end{lstlisting}

For parameterized types, the generated instance takes serializers for type
parameters.  For recursive types, the generated encoder and decoder use
structurally recursive definitions.  The current implementation also supports a
conservative collection of nested recursive occurrences through standard data
containers such as lists, options, and products.  More general nested or
mutually recursive types are currently reported as unsupported rather than
handled partially.\footnote{The issue of generating quality \texttt{to/from\_JSON} functions is not as difficult as proving them correct without quality structural recursion procedures. This may be mitigated as better support for nested inductives in Rocq is actively being pursued \cite{Lamiaux:2026:Rocq-Nested-Inductives}}

\begin{lstlisting}[language=Coq]
Inductive BinTree (A : Type) : Type :=
| BinLeaf
| BinNode (left : BinTree A) (value : A) (right : BinTree A).
Elpi derive.jsonifiable BinTree.
Check BinTree_Jsonifiable : \forall A, Jsonifiable A -> Jsonifiable (BinTree A).
\end{lstlisting}

Failures are reported as ordinary Rocq errors whose message names the blocking
shape when it is recognized.  For example, attempting to derive an instance for
\texttt{sig} fails with:

\begin{lstlisting}
Error:
derive.jsonifiable: dependent constructor fields are not supported by
Jsonifiable. Field: ... type head: unknown type constructor
\end{lstlisting}

The benchmark script used in Section~\ref{sec:evaluation} also acts as a
batch diagnostic pass over installed Corelib/Stdlib sources: it records the
failure category, source location, generated probe file, and complete Rocq log
for every candidate.
% The standalone user interface is intentionally smaller;
% it does not yet provide a separate lint command that predicts derivability
% without attempting the derivation.

The generated proof is part of the public contract.  A successful derivation
does not merely produce functions with plausible behavior; it registers a
\texttt{canonical\_jsonification} proof.  This property is intentionally
one-sided.  It says that values produced by the encoder can be decoded back to
the original value.  For extracted verified components that emit JSON for other
tools or services, this is the direction that protects the boundary: the
serialized message has not lost or changed the Rocq value.  The converse
property, that every accepted JSON value is a canonical representation, is a
different contract.  It would require specifying a canonical JSON grammar for
each type and proving that the decoder rejects all non-canonical alternatives,
which is useful but substantially more representation-specific.

\section{Implementation}

The deriver follows the shape of the Rocq declaration.  ELPI is an embedded
$\lambda$Prolog language used by \coqelpi to inspect and construct Rocq terms at
the meta-level.  The deriver first reads the inductive or record view,
classifies parameters and constructor arguments, and then builds separate
skeletons for the encoder, decoder, proof, and final typeclass instance.  The
skeletons are elaborated by Rocq before being added as constants.  This staging
has been useful in practice: ELPI performs structural analysis and code
generation, while Rocq remains responsible for checking the terms that become
part of the trusted development.

Two engineering choices are central.  First, field serializers are kept
abstract through typeclass arguments where possible.  This makes generated
instances compose with existing hand-written or derived instances, including
standard containers. In practice, this means that although \lstinline|nat| in Rocq is inductively defined as \lstinline[language=Coq]{O | S _}, we are better served by making it an actual number (e.g. 0, 1, 42).
Second, decoder generation is performance-sensitive.
Large enumerations are decoded using a string decision tree that extracts to
direct pattern matching over characters, avoiding a long chain of string
equality tests.  The resulting extracted code is close to the shape a careful
and performance oriented user would write by hand.

The proof-generation strategy is mixed.  General recursive and record cases use
Rocq proof automation specialized to the generated encoders and decoders.  Pure
enumerations use a direct generated proof term, avoiding proof-search overhead
on a common stress case.  This division is not theoretically deep, but it
matters for predictable tool latency.

\section{Evaluation}
\label{sec:evaluation}

We evaluate two questions: how broadly the deriver applies to existing Rocq
declarations, and whether generated extracted code is competitive with
hand-written code on stress cases.

\subsection{Applicability}

The artifact includes a benchmark script that scans installed Corelib and
Stdlib sources for inductive-like declarations, probes each candidate in
isolation, records diagnostics, and then compiles a single benchmark file
containing all successful derivations.  This workflow is deliberately
conservative: unsupported declarations remain visible as categorized failures.
Declarations that are visible in source but are not closed derivation targets,
such as declarations inside functor bodies or module signatures, are recorded
separately rather than discarded.

\begin{table}
  \centering
  \caption{Corelib/Stdlib applicability and failure categories.}
  \label{tab:applicability}
  \small
  \begin{minipage}[t]{0.47\linewidth}
    \centering
    \begin{tabular}{p{0.72\linewidth}r}
      \toprule
      Metric                       & Count                        \\
      \midrule
      Discovered declarations      & \JsonifiableDiscovered       \\
      Recorded, not probed         & \JsonifiableSkipped          \\
      Probed declarations          & \JsonifiableProbed           \\
      Successful probes            & \JsonifiableProbeSuccesses   \\
      Probe failures               & \JsonifiableProbeFailures    \\
      Probe timeouts               & \JsonifiableProbeTimeouts    \\
      Timed successful derivations & \JsonifiableTimedDerivations \\
      \bottomrule
    \end{tabular}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.47\linewidth}
    \centering
    \begin{tabular}{p{0.78\linewidth}r}
      \toprule
      Failure category & Count \\
      \midrule
      \JsonifiableFailureRows
      \bottomrule
    \end{tabular}
  \end{minipage}
\end{table}

The successful probes include \JsonifiableSuccessInductives{} inductives,
\JsonifiableSuccessVariants{} variants, and \JsonifiableSuccessRecords{}
records or structures; \JsonifiableSuccessCorelib{} are from Corelib and
\JsonifiableSuccessStdlib{} are from Stdlib.

The category names in Table~\ref{tab:applicability} are a triage device, not a
claim that every failed probe is a tool defect.  Some declarations are clear
non-targets for serialization: propositions are erased by extraction, functions
have no canonical JSON representation, sort-valued fields contain types rather
than values, and coinductive values may be infinite.  The genuine current
limitations are concentrated around dependent data, where decoding must
reconstruct values whose types depend on earlier fields or external indices.
Table~\ref{tab:failure-examples} gives one representative declaration for each
category and the rationale used by the artifact.

\begin{table}
  \centering
  \caption{Representative failure examples and classification rationale.}
  \label{tab:failure-examples}
  \scriptsize
  \setlength{\tabcolsep}{3pt}
  \begin{tabular}{p{0.43\linewidth}p{0.53\linewidth}}
    \toprule
    Category and example & Rationale                                                                                                  \\
    \midrule
    \texttt{prop-target-not-supported}: \texttt{or}
                         & The target lives in \texttt{Prop}; propositions are erased at extraction and are not runtime data.         \\
    \texttt{dependent-field-not-supported}: \texttt{sig}
                         & A later field depends on an earlier witness; decoding must reconstruct a value and its dependent type.     \\
    \texttt{indexed-family-not-supported}: \texttt{reflect}
                         & The declaration is indexed by values; decoding requires recovering the index or fixing it in the instance. \\
    \texttt{function-field-not-supported}: \texttt{implies}
                         & Arbitrary functions have no canonical data representation in JSON or ordinary serializers.                 \\
    \texttt{proof-field-not-supported}: \texttt{sumbool}
                         & A computational wrapper carries proof evidence; decoding requires proof erasure or reconstruction.         \\
    \texttt{sort-field-not-supported}: \texttt{Tlist}
                         & Constructor fields contain sorts such as \texttt{Type}; these are types, not JSON values.                  \\
    \texttt{coinductive-not-supported}: \texttt{Stream}
                         & Potentially infinite data needs an explicit depth-bounded or lazy serialization contract.                  \\
    \bottomrule
  \end{tabular}
\end{table}

The important distinction is between non-targets and genuine engineering
limitations.  The non-target group is not a design choice particular to
\texttt{rocq-json}: there is simply no runtime proposition to serialize after
extraction; arbitrary functions do not have a canonical finite data
representation; sorts such as \texttt{Type} and \texttt{Set} are not ordinary
values; and coinductive data needs a separate bounded or lazy contract.  These
account for 158 probe failures.  The remaining large categories are dependent
fields and indexed families, 69 cases in total.  Those are real future work:
the JSON decoder would have to recover enough information to reconstruct a
dependent value, or the deriver would need a fixed-index or sigma-style
encoding.  The three proof-field cases sit on the same boundary: the outer type
is computational, but successful decoding would require erasing or rebuilding
proof evidence that extraction normally removes.  The
\JsonifiableSkipped{} recorded-but-not-probed declarations are reported in the
artifact as well: \JsonifiableSkippedParameterizedModule{} occur inside
parameterized modules or functor bodies, such as
\texttt{Stdlib.FSets.FMapAVL.Raw.tree}, and
\JsonifiableSkippedModuleType{} occur inside module types or signatures, such
as \texttt{MSetGenTree.Ops.tree}.  These are genuine source declarations, but
not closed global references to which the deriver can be applied directly
\emph{outside the functor}.  All categories are reported explicitly so the
success rate is clear and auditable.

The raw success rate is therefore intentionally not the main applicability
claim.  Of the \JsonifiableDiscovered{} discovered declarations, the
\JsonifiableSkipped{} functor/signature declarations are not closed deriver
inputs, and 158 probe failures are non-targets in the sense above.  The
meaningful remaining gap is the dependent fragment: dependent fields, indexed
families, and proof-bearing computational wrappers.  This is also the fragment
where extraction itself erases part of the proof context, so serializing the
``whole'' dependent value is not always the right deployment contract.  The
artifact reports these cases explicitly rather than folding them into an
undifferentiated failure count.
Excluding the \JsonifiableSkipped{} functor/signature declarations that are not
valid deriver inputs and the 158 non-target declarations, the tool successfully
derives instances for \JsonifiableProbeSuccesses{} of 153 semantically eligible
declarations, roughly 53\% coverage on the well-defined target fragment, with
the remaining gap concentrated in dependent and indexed types.

\subsection{Derivation Time}

The combined successful benchmark records Rocq's \texttt{Time} output for each
derived instance.  In the reported run, the combined
benchmark compiled successfully with wall-clock time
\JsonifiableBenchmarkWallSeconds{} seconds; the sum of Rocq-reported derivation
transactions was \JsonifiableDerivationSumSeconds{} seconds.  The mean
derivation time was \JsonifiableDerivationMeanSeconds{} seconds, the median was
\JsonifiableDerivationMedianSeconds{} seconds, the 90th percentile was
\JsonifiableDerivationPNineZeroSeconds{} seconds, and the maximum was
\JsonifiableDerivationMaxSeconds{} seconds.

\begin{table}
  \centering
  \caption{Slowest successful derivations in the broad benchmark.}
  \begin{tabular}{l @{\hspace{0.25cm}} lr}
    \toprule
    Declaration & Kind & Seconds \\
    \midrule
    \JsonifiableSlowestRows
    \bottomrule
  \end{tabular}
\end{table}

The slowest success is \texttt{byte}, a 256-constructor Corelib enumeration.  It
is the broad benchmark's version of the large enum stress case used while
engineering the string decision tree.  The remaining cost is dominated by
Rocq-side derivation and proof construction.
After extraction, the corresponding
dispatch path is close to the handwritten Rocq baseline below.

\subsection{Extracted Code Performance}

The extraction benchmark compares generated definitions against handwritten
Rocq definitions after both have been extracted to OCaml.  This keeps the
comparison in the same source language and extraction pipeline.  The benchmark
covers several shapes: a 256-constructor enumeration, a tuple-like constructor,
a flat record, two mixed sums with nullary and field-bearing constructors, and a
recursive binary tree.  Each benchmark was run
\JsonifiableExtractionGeneratedRuns{} times.  The enum benchmark serializes and
deserializes every constructor; the other benchmarks run many iterations over
representative values.

\begin{table}
  \centering
  \caption{Extracted round-trip benchmarks.}
  \label{tab:extraction}
  \begin{tabular}{lrrr}
    \toprule
    Benchmark & Generated mean (ms) & Handwritten mean (ms) & Change (\%) \\
    \midrule
    \JsonifiableExtractionComparisonRows
    \bottomrule
  \end{tabular}
\end{table}

Negative changes in Table~\ref{tab:extraction} mean the generated code is
faster than the handwritten baseline.
These benchmarks do not predict every serializer workload, but instead
validate the main engineering concern: generated instances should extract
to code with the same general performance profile as direct
handwritten Rocq definitions.
The handwritten baselines were written by the authors in Rocq and extracted
through the same pipeline; they were not independently optimized.  The
comparison should therefore be read as evidence that generated code avoids
obvious extraction-time performance regressions, not as a claim of superiority
over all possible handwritten serializers or OCaml-specific deriving systems.

\section{Related Work and Positioning}

Rocq has several metaprogramming routes for deriving boilerplate.  MetaCoq~\cite{Sozeau:2020:Metacoq} provides quoted syntax and verified
metaprogramming; \coqelpi provides an embedded $\lambda$Prolog language
integrated with Rocq elaboration and an existing derive framework.
\texttt{rocq-json} uses \coqelpi because the task is structural inspection plus
term construction, with the generated terms checked by Rocq.  MetaCoq could in
principle support a more deeply verified metaprogram through the
SafeTemplateMonad; the tradeoff here is pragmatic.  The trusted result is not
the ELPI program itself, but the generated Rocq constants and the
\texttt{canonical\_jsonification} theorem that Rocq accepts.  This matches the
engineering goal of producing executable boundary code and a checked contract
with low user overhead. In particular, the use of ELPI allows efficient
generation of the \lstinline|Jsonifiable| instances, as well as hooking
into the general ``deriviation'' framework.

\coqelpi already includes a derive framework and examples of type-directed
derivers for logical or structural boilerplate.  Compared with typical derivers
for equality, ordering, showing, decidability, or logical instances,
\texttt{rocq-json} generates two executable programs and a theorem relating
them.  That proof obligation changes the problem: it is not enough to inspect
constructors and print code, because the generated encoder and decoder must be
accepted together with an invertibility proof.

This work is also distinct from Rocq/JSON infrastructure such as SerAPI~\cite{GallegoArias:2016:SerAPI}.  SerAPI serializes Rocq's own syntax and
protocol data for interaction with external clients; \texttt{rocq-json} derives
verified \lstinline|Jsonifiable| instances for user-defined Rocq data types.

Lean provides JSON datatypes and typeclass-based
derivation facilities in its programming environment~\cite{moura2015lean,Lean4Json} through the \texttt{deriving} system.
These ecosystems support
practical serialization workflows, but the serialization layer is not normally
accompanied by a proof, at the source proof-assistant level, that decoding the
encoded value recovers the original user datatype.

OCaml libraries such as \texttt{ppx\_yojson\_conv}
generate efficient JSON code for production datatypes~\cite{PpxYojsonConv}.
These systems are practical and often highly optimized, but they critically do not produce
a Rocq-checked theorem tied to the source inductive or record declaration.  The
substantially new combination here is generated encoder, generated decoder,
checked encode-decode theorem, extraction-conscious code shape, and a
reproducible artifact that reports both successes and limitations.

% \section{Artifact}

% The artifact is provided in the form of a \texttt{opam} installable and distributable project. \texttt{dune} can be used to build the main
% project, runs the Corelib/Stdlib applicability benchmark, runs the
% extraction benchmark, and regenerates the LaTeX result macros used in this
% paper.  The generated JSON summary, CSV files, and Markdown failure report are
% included as inspection points: the summary gives aggregate counts, the CSV files
% give row-level data, and the failure report records representative diagnostics
% for each category.

\section{Limitations and Future Work}

The current deriver targets computational data in \texttt{Type} or
\texttt{Set}.  It deliberately excludes shapes where serialization is not a
well-defined request: propositions are not runtime values after extraction,
functions have no canonical finite data representation, sort-valued fields
contain types rather than values, and coinductive values require a separate
bounded or lazy contract.  These exclusions are not merely conservative
engineering choices; they follow from the operational meaning of the values.

The remaining limitations are mostly dependent-type limitations.  The deriver
does not yet support dependent families, indexed families, or records whose
field types depend on earlier fields.  Some nested recursion through standard
containers is supported, but arbitrary nested and mutually recursive types remain
outside the current design.

The JSON representation is also intentionally modest.  The paper evaluates the
\emph{derivation method and the certified round-trip property}, not complete
adherence to the JSON RFC or interoperability with every external JSON parser.

The main extensions are indexed families, proof-bearing data, and deeper
library discovery.  Indexed families may require fixed-index instances or
dependent-pair decoding; proof fields likely require erasure plus user-supplied
reconstruction lemmas.  More generally, support for dependent data should make
the extraction boundary explicit: when proofs or indices are erased at runtime,
the right JSON format may be a projection of the computational content rather
than a serialization of the full source-level dependent value.  A Rocq-assisted
discovery phase could classify module scopes directly from Rocq's environment
rather than relying on source syntax.

\section{Conclusion}

\texttt{rocq-json}'s ELPI deriver demonstrates that boundary code for extracted
verified components can be treated as part of the formal artifact.  The
generated instances combine executable encoders and decoders with Rocq-checked
invertibility proofs, apply across a meaningful fragment of existing library
declarations, and extract to competitive code on the evaluated examples.
The broader lesson is that certified derivation tools can be utilized in
verification efforts to generate performant code \emph{without} leaving
the assurance boundary.

\bibliographystyle{splncs04}
\bibliography{bib/sldg}

\newpage
\appendix

\section{Round-Trip Benchmark Rocq Code}

The extracted-code benchmarks in Table~\ref{tab:extraction} are defined in the
extraction benchmark source.  The generated cases use
\texttt{Elpi derive.jsonifiable}; the primed instances below are the handwritten
Rocq baselines extracted and timed by the same harness.

\subsection{Benchmark Types}

\lstinputlisting[
  language=Coq,
  firstline=26,
  lastline=45,
  breaklines=true,
  basicstyle=\ttfamily\scriptsize
]{../extracting/JSON_Derive_Tests.v}

\lstinputlisting[
  language=Coq,
  firstline=68,
  lastline=76,
  breaklines=true,
  aboveskip=0pt,
  belowskip=0pt,
  basicstyle=\ttfamily\scriptsize
]{../extracting/JSON_Derive_Tests.v}

\lstinputlisting[
  language=Coq,
  firstline=165,
  lastline=168,
  breaklines=true,
  aboveskip=0pt,
  belowskip=0pt,
  basicstyle=\ttfamily\scriptsize
]{../extracting/JSON_Derive_Tests.v}

\lstinputlisting[
  language=Coq,
  firstline=425,
  lastline=458,
  breaklines=true,
  aboveskip=0pt,
  belowskip=0pt,
  basicstyle=\ttfamily\scriptsize
]{../extracting/JSON_Derive_Tests.v}

\subsection{Handwritten Rocq Baselines}

\lstinputlisting[
  language=Coq,
  firstline=257,
  lastline=383,
  breaklines=true,
  aboveskip=0pt,
  belowskip=0pt,
  basicstyle=\ttfamily\scriptsize
]{../extracting/JSON_Derive_Tests.v}

\lstinputlisting[
  language=Coq,
  firstline=461,
  lastline=471,
  breaklines=true,
  aboveskip=0pt,
  belowskip=0pt,
  basicstyle=\ttfamily\scriptsize
]{../extracting/JSON_Derive_Tests.v}
$$\vdots$$
\lstinputlisting[
  language=Coq,
  firstline=590,
  lastline=601,
  breaklines=true,
  aboveskip=0pt,
  belowskip=0pt,
  basicstyle=\ttfamily\scriptsize
]{../extracting/JSON_Derive_Tests.v}
$$\vdots$$
\lstinputlisting[
  language=Coq,
  firstline=720,
  lastline=724,
  breaklines=true,
  aboveskip=0pt,
  belowskip=0pt,
  basicstyle=\ttfamily\scriptsize
]{../extracting/JSON_Derive_Tests.v}

\subsection{Extraction Command}

\lstinputlisting[
  language=Coq,
  firstline=726,
  lastline=734,
  breaklines=true,
  aboveskip=0pt,
  belowskip=0pt,
  basicstyle=\ttfamily\scriptsize
]{../extracting/JSON_Derive_Tests.v}

\end{document}
